Bathtub Qualitative Reasoning

### 2016-10-17 paper.tex
paper

>>>>

\begin{itemize}
\item \textbf{Quantities:}
\begin{itemize}
\item Inflow (of water into the container) $\in [0, +]$
\item Outflow (of water out of the container) $\in [0, +, Max]$
\item Volume (of the water in the container) $\in [0, +, Max]$
\end{itemize}

\item \textbf{Dependencies:}

\begin{itemize}
\item I+(Inflow, Volume): the amount of inflow increases the volume
\item I-(Outflow, Volume): the amount of outflow decreases the volume
\item P+(Volume, Outflow): outflow changes are proportional to volume changes
\item V(Volume(Max), Outflow(Max)): the outflow is at its highest value (Max), when the volume is at it highest value
\item V(Volume(0), Outflow(0)): there is no outflow, when there is no volume
\end{itemize}
\end{itemize}
